Title

### 2023-08-02 paper/paper.tex
papaer

\documentclass[12pt, letterpaper, twocolumn]{article}
\title{Title}
\author{Author}
\date{Date}

@@

\onecolumn
\begin{table}[h]
\centering
\begin{tabular}{|c c c|} 
    \hline
    Name & input length & embedding dimension  \\ 
    \hline
    embedding reproduction (rep)        & 64    & 64    \\
    dnabert                             & 512     & 768  \\
    prose                               & 545   & 100    \\
    alphafold                           & 1024   & 18744 \\
    evolutionary scale modeling (esm)   & 1024    & 1280 \\  
    \hline
\end{tabular}
\caption{Table to test captions and labels.}
\label{table:data}
\end{table}
\twocolumn

@@

>>>>

\documentclass[12pt, letterpaper, twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{placeins}

\title{Title}
\author{Author}
\date{Date}

@@

\onecolumn
\begin{table}[h]
\centering
\begin{tabular}{|l c c|} 
    \hline
    Name & input length & embedding dimension  \\ 
    \hline
    embedding reproduction (rep)\cite{yang2018learned}       & 64    & 64    \\
    dnabert \cite{ji2021dnabert}                     & 512     & 768  \\
    prose   \cite{bepler2021learning}                   & 512   & 100    \\
    alphafold  \cite{jumper2021highly}                 & 1024   & 384 \\
    evolutionary scale modeling (esm2) \cite{lin2022language}   & 1024    & 1280 \\  
    \hline
\end{tabular}
\caption{Embedders used in the experiments.}
\label{table:data}
\end{table}
\twocolumn

@@

\onecolumn
\newpage
\FloatBarrier
\bibliographystyle{plain}
\bibliography{bibliography}
